timesliced_random_cell_selection

### 2018-11-08 src/raster_sjl.Rmd
exploration of looping through several years and months that are the same...

netcdf_list <- list.files("../data/env/testnetcdf/salinity", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/env/testnetcdf/salinity", pattern = '*.nc', full.names = FALSE) #false means the path is not included
for (i in 1:no_netcdf){  
  print(netcdf_name[i]) #this just prints the name of the netCDF R is working on
  brkyr <- sapply(strsplit(netcdf_name[i], "_"), "[[", 1) # extracting the first part of the netcdf filename (which is the year)
  brkmth <- sapply(strsplit(netcdf_name[i], "_"), "[[", 2) # extracting the second part of the netcdf filename (which is the month)
  temp_brick <- brick(netcdf_list[i], lvar = 4)
  temp_brick <- projectRaster(temp_brick, aea) 
    for (j in 1:length(obssp)) {  
      print(j)
      de <- obssp$depth[[j]]  # a variable for the observation depth layer
      yr <- obssp$year[j]  # a variable for the observation year
      mth <- obssp$month[j]  # a variable for the observation month
      #I think i need an if statement here... if brkyr == yr & brkmth == mth do the data extraction below
        if (brkyr == yr & brkmth == mth){
          obssp$salinity_depth[j] <- extract(x=temp_brick[[de]], y = obssp) 
          obssp$salinity_surface[j] <- extract(x=temp_brick[[1]], y = obssp)
        }
    }
}
obssp$salinity_depth
obssp$salinity_surface

>>>>

```{r}
obs <- read.csv("../data/observationslong.csv", header = TRUE) #change this path to your .csv location
#obs$month <- sprintf("%02d",obs$month) # new addition to add the 0 infront of single digit... test for seeing if you can match the netcdf name for year month selection of bricks
xy <- obs[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
obssp <- SpatialPointsDataFrame(coords = xy, data = obs, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
```

```{r}
obssp$salinity_depth
obssp$salinity_surface
```
output is  
> obssp$salinity_surface
[1] 32.82551 33.19321 32.18221 32.23423 32.61295 32.61270 32.39069
> obssp$salinity_depth
[1] 32.83107 33.19973       NA 32.51381       NA 32.61270 32.39358

next step - check to see if the values are correct (particularly interested in those NA...)

```{r}
plot(temp_brick[[40]])
```
for the NA - of course - the layer no longer exists at that depth (water shallower than that)
